### 2025-07-15 multiple-regression.qmd
20250712 - tweaks
20250715 - load beta regression model from OSF

::: {#nte-bayesianBetaRegression .callout-note title="Bayesian beta regression"}
Note: the following code that runs the model takes a while.
:::

```{r}
#| label: beta-regression
#| output: false

@@

@@

We set up the bootstrap folds using the `bootstraps()` function of the `rsample` package [@R-sample].

>>>>

::: {#nte-bayesianBetaRegression .callout-note title="Bayesian beta regression"}
Note: the following code that runs the model takes a while.
If you just want to save time and load the model object instead of running the model, you can load the model object (which has already been fit) using this code:

```{r}
load(url("https://osf.io/download/fe37j/"))
```
:::

```{r}
#| label: beta-regression
#| output: false
#| eval: false

@@

save(
  betaRegression,
  file = "./data/betaRegression.RData")
```

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/betaRegression.RData", fsep = ""))
```

load(url("https://osf.io/download/fe37j/"))
```

@@

We set up the bootstrap folds using the `bootstraps()` function of the `rsample` package [@R-rsample].
